---
title: "Peer Assessment 2"
author: "Francisco J. Garcia R."
date: "Tuesday, August 19, 2014"
output:
    html_document:
        theme: cerulean
---

##Synopsis 
Synopsis: Immediately after the title, there should be a synopsis which describes and summarizes your analysis in at most 10 complete sentences.


##Data Processing
There should be a section titled Data Processing which describes (in words and code) how the data were loaded into R and processed for analysis. In particular, your analysis must start from the raw CSV file containing the data. You cannot do any preprocessing outside the document. If preprocessing is time-consuming you may consider using the cache = TRUE option for certain code chunks.

### Initial configuration

The goal of this section is create some variables that will be used for processing data

```{r echo=TRUE}
#Variables
urlData <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
DataFile_bz2 <- "repdata_data_StormData.csv.bz2"
DataFileCsv <- "repdata_data_StormData.csv"

#Pre-requisites:
IsRutilsInstalled <- require("R.utils")
if(!IsRutilsInstalled){
    install.packages("R.utils")
    library(R.utils)
}

```

### Getting data
1. Download compressed file
2. Extract file
3. Load data into  `OriginalData`

```{r echo=TRUE, cache=TRUE, cache.lazy=TRUE}
GettingData <- function(){
    #Download compressed file
    if(!file.exists(DataFile_bz2)){
        download.file(urlData, DataFile_bz2)
        }
    
    #extract CSV data
    if(!file.exists(DataFileCsv)){
        bunzip2(DataFile_bz2, destname=DataFileCsv, overwrite=TRUE, remove=TRUE)
        }
    
    #Read Data
    if(file.exists(DataFileCsv)){
        OriginalData <- read.csv(DataFileCsv)
        OriginalData
        }else{
             NULL
            }
    }

OriginalData <- GettingData();
```
### cleaning data

```{r echo=TRUE}
head(OriginalData)
```


##Results 
There should be a section titled Results in which your results are presented.

##Aditional info
For debugging purposes, the specification of the machine:
```{r echo=TRUE}
sessionInfo()
```

